\LARGE \bf Simultaneous Hand-Eye and Robot-World Calibration by Solving the AX=YB Problem without Correspondence*

### 2015-11-22 DrC Version 1/root1.tex
Change of format to fit into the eight pages limit

Starting with Eq.(\ref{equ9}), performing a convolution on both of the left sides of the equation with
$\delta_{Y^{-1}}(H)$, and using the associativity of convolution, we will have:
\begin{equation} 
(\delta_{Y^{-1}} * f_A * \delta_X)(H) = f_B(H).
\label{equ18new}
\end{equation}
Use the definition of mean as in Eq.~(\ref{equ11}) along with Eq.~(\ref{equ18new}), we have 
$$ \int_{SE(3)} \log({M}_{B}^{-1} H) f_B(H) dH = $$
$$ \int_{SE(3)} \log({M}_{B}^{-1} H) (\delta_{X^{-1}} * f_A * \delta_{X})(H) dH = $$
\begin{equation}
\int_{SE(3)} \log({M}_{B}^{-1} H) f_A({Y} H {X}^{-1}) dH = \mathbb{O}.
\label{equ19new}
\end{equation}
Change the variable as $K = {Y} H {X}^{-1}$ and use the invariance of integration \cite{chirikjian2011stochastic}, then Eq.~(\ref{equ19new}) becomes:
\begin{equation}
\int_{SE(3)} \log({M}_{B}^{-1} Y^{-1} K X) f_A(K) dK = \mathbb{O}. 
\label{equ20new}
\end{equation}
which falls into the form of the mean definition of $\{A_i\}$.
If we further multiply $X$ and $X^{-1}$ on the left and right of both sides of Eq.~(\ref{equ20new}), then $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(M_{A}^{-1}K)$.
Knowing that $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(X {M}_{B}^{-1} Y^{-1} K)$, and we have 
$X {M}_{B}^{-1} Y^{-1} = M_{A}^{-1}$ which is equivalent to Eq.~(\ref{equ15a}),

@@

In the above approach, we used Eq.~(\ref{equ15b}) to calculate $X_k$ and Eq.~(\ref{equ15a}) to obtain the corresponding $Y_k$. However, we now show that one can calculate the eight candidates of $Y$ independently and employ Eq.~(\ref{equ15a}) as a constraint to filter out the optimal $\{X, Y\}$ pair.

Given the equation $AX=YB$, apply an inverse on both sides of the equation and we will have $B^{-1}Y^{-1} = X^{-1}A^{-1}$. Following the same derivations from Eq.~(\ref{equ5}) to Eq.~(\ref{equ15b}), we have:
\begin{IEEEeqnarray}{l}
M_{B^{-1}} Y^{-1} = X^{-1} M_{A^{-1}} \IEEEyessubnumber\label{equ33a}
\\*
Ad(Y)\Sigma_{B^{-1}}Ad^{T}(Y) = \Sigma_{A^{-1}}. \IEEEyessubnumber\label{equ33b}
\end{IEEEeqnarray}
Similarly, Eq.~(\ref{equ33b}) can give eight candidates of $Y^{-1}$, or equivalently, the eight candidates of $Y$. Let $X_{k1}$ where $k1 = 1,2, \cdots, 8$ denote the $X$s obtained from Eq.~(\ref{equ15b}) and $Y_{k2}$ where $k2 = 1,2,\cdots, 8$ denote the $Y$s obtained from Eq.~(\ref{equ33b}), and we can use Eq.~(\ref{equ15a}) and Eq.~(\ref{equ33a}) to form a minimization problem as:
\begin{equation}
\underset{k1, k2}{min} ||M_A X_{k1} - Y_{k2} M_B ||_F + ||M_B^{-1} Y^{-1}_{k2} - X^{-1}_{k1} M_A^{-1} ||_F
\end{equation}
which can give the optimal $(X_{k1}, Y_{k2})$ pair. We call this approach the \textit{prob} method, and compare it with Li's method for testing its effectiveness of handling scrambled data sets. For simplicity, we use Eq.~(\ref{equ33a}) and Eq.~(\ref{equ33b}) to generate $\{B_i\}$, whereas compute $\{A_i\}$ using $A_i = X^{-1} Y B_i$ without exerting noise on $B_i$. Then $\{A_i\}$ is scrambled at each percentage from $0\%$ up to $100\%$. 50 times of simulations are performed for each percentage rate and the same error metrics are used as in Section \ref{sect5}. As shown in Fig.~(\ref{fig7}) and Fig.~(\ref{fig8}), as the percentage of scrambled data goes up, the errors in rotation and translation for Li's method gradually diverge, while the errors for the $prob$ method are very stable and small. This shows the significant advantage of the probabilistic method in handling disordered data sets. However, Li's method is still more accurate when the exact correspondence is known between $\{A_i\}$ and $\{B_i\}$.

>>>>

Starting with Eq.(\ref{equ9}), performing a convolution on both of the left sides of the equation with
$\delta_{Y^{-1}}(H)$, and using the associativity of convolution, we will have:
\begin{equation} 
(\delta_{Y^{-1}} * f_A * \delta_X)(H) = f_B(H).
\label{equ18new}
\end{equation}
Use the definition of mean as in Eq.~(\ref{equ11}) along with Eq.~(\ref{equ18new}), we have 
$$ \int_{SE(3)} \log({M}_{B}^{-1} H) f_B(H) dH = $$
$$ \int_{SE(3)} \log({M}_{B}^{-1} H) (\delta_{X^{-1}} * f_A * \delta_{X})(H) dH = $$
\begin{equation}
\int_{SE(3)} \log({M}_{B}^{-1} H) f_A({Y} H {X}^{-1}) dH = \mathbb{O}.
\label{equ19new}
\end{equation}
Change the variable as $K = {Y} H {X}^{-1}$ and use the invariance of integration \cite{chirikjian2011stochastic}, then Eq.~(\ref{equ19new}) becomes:
\begin{equation}
\int_{SE(3)} \log({M}_{B}^{-1} Y^{-1} K X) f_A(K) dK = \mathbb{O}. 
\label{equ20new}
\end{equation}
which falls into the form of the mean definition of $\{A_i\}$.
If we further multiply $X$ and $X^{-1}$ on the left and right of both sides of Eq.~(\ref{equ20new}), then $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(M_{A}^{-1}K)$.
Knowing that $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(X {M}_{B}^{-1} Y^{-1} K)$, and we have 
$X {M}_{B}^{-1} Y^{-1} = M_{A}^{-1}$ which is equivalent to Eq.~(\ref{equ15a}). Eq.(\ref{equ15b}) follows from \cite{wang2008nonparametric} because the F(A,B) term has products of covariances of the functions being convolved, and delta functions have zero covariance so the F term is zero.

@@

In the above approach, we used Eq.~(\ref{equ15b}) to calculate $X_k$ and Eq.~(\ref{equ15a}) to obtain the corresponding $Y_k$. However, we now show that one can calculate the eight candidates of $Y$ independently and employ Eq.~(\ref{equ15a}) as a constraint to filter out the optimal $\{X, Y\}$ pair. Given the equation $AX=YB$, apply an inverse on both sides of the equation and we will have $B^{-1}Y^{-1} = X^{-1}A^{-1}$. Following the same derivations from Eq.~(\ref{equ5}) to Eq.~(\ref{equ15b}), we have:
\begin{IEEEeqnarray}{l}
M_{B^{-1}} Y^{-1} = X^{-1} M_{A^{-1}} \IEEEyessubnumber\label{equ33a}
\\*
Ad(Y)\Sigma_{B^{-1}}Ad^{T}(Y) = \Sigma_{A^{-1}}. \IEEEyessubnumber\label{equ33b}
\end{IEEEeqnarray}
Similarly, Eq.~(\ref{equ33b}) can give eight candidates of $Y^{-1}$, or equivalently, the eight candidates of $Y$. Let $X_{k1}$ where $k1 = 1,2, \cdots, 8$ denote the $X$s obtained from Eq.~(\ref{equ15b}) and $Y_{k2}$ where $k2 = 1,2,\cdots, 8$ denote the $Y$s obtained from Eq.~(\ref{equ33b}), and we can use Eq.~(\ref{equ15a}) and Eq.~(\ref{equ33a}) to form a minimization problem as:
\begin{equation}
\underset{k1, k2}{min} ||M_A X_{k1} - Y_{k2} M_B ||_F + ||M_B^{-1} Y^{-1}_{k2} - X^{-1}_{k1} M_A^{-1} ||_F
\end{equation}
which can give the optimal $(X_{k1}, Y_{k2})$ pair. We call this approach the \textit{prob} method, and compare it with Li's method for testing its effectiveness of handling scrambled data sets. For simplicity, we use Eq.~(\ref{equ33a}) and Eq.~(\ref{equ33b}) to generate $\{B_i\}$, whereas compute $\{A_i\}$ using $A_i = X^{-1} Y B_i$ without exerting noise on $B_i$. Then $\{A_i\}$ is scrambled at each percentage from $0\%$ up to $100\%$. 50 times of simulations are performed for each percentage rate and the same error metrics are used as in Section \ref{sect5}. As shown in Fig.~(\ref{fig7}) and Fig.~(\ref{fig8}), as the percentage of scrambled data goes up, the errors in rotation and translation for Li's method gradually diverge, while the errors for the $prob$ method are very stable and small. This shows the significant advantage of the probabilistic method in handling disordered data sets. However, Li's method is still more accurate when the exact correspondence is known between $\{A_i\}$ and $\{B_i\}$.
